### 2018-09-10 Sections/errors_in_quantum_networks.tex
minor

The scaling of loss over distance $d$ varies depending on the medium through which the light traverses. When propagating through fibre, atmosphere, or some other lossy medium, net efficiency scales inverse exponentially as,
\begin{align}
	\eta = O(e^{-\alpha d}),
\end{align}
where $\alpha$ is a characteristic of the medium\footnote{With present-day fibre technology, this characteristic decay rate is on the order of \mbox{$\alpha = \frac{1}{22\mathrm{km}}$}.}. In space on the other hand, where the medium of propagation is vacuum, which is effectively lossless, the effective loss rate is not determined by the medium, but rather by the fact that the spot-size\index{Spot-size} of an optical state is subject to dispersion\index{Dispersion} and grows only quadratically with distance. Then when the light is detected, if the spot-size is greater than the detector aperture, the undetected component effectively translates to loss. Thus through free-space the effective efficiency scales as,
\begin{align}
	\eta = O\left(\frac{1}{d^2}\right),
\end{align}
which is far more favourable than the exponential scaling inherent to lossy mediums. This provides space-based quantum networks with an inherent competitive advantage compared to any form of ground-based network.

>>>>

The scaling of loss over distance $d$ varies depending on the medium through which the light traverses. When propagating through fibre, atmosphere, or some other lossy medium, net efficiency scales inverse exponentially as,
\begin{align}
	\eta = O(e^{-\alpha d}),
\end{align}
where $\alpha$ is a characteristic of the medium\footnote{With present-day fibre technology, this characteristic decay rate is on the order of \mbox{$\alpha = 22\mathrm{km}^{-1}$}.}. In space on the other hand, where the medium of propagation is vacuum, which is effectively lossless, the effective loss rate is not determined by the medium, but rather by the fact that the spot-size\index{Spot-size} of an optical state is subject to dispersion\index{Dispersion} and grows only quadratically with distance. Then when the light is detected, if the spot-size is greater than the detector aperture, the undetected component effectively translates to loss. Thus through free-space the effective efficiency scales as,
\begin{align}
	\eta = O\left(\frac{1}{d^2}\right),
\end{align}
which is far more favourable than the exponential scaling inherent to lossy mediums. This provides space-based quantum networks with an inherent competitive advantage compared to any form of ground-based network.
